oolong: An R package for validating  automated content analysis tools

### 2020-07-21 paper/paper.rmd
fix small grammatical problems, ref #31

This package focuses on semantic validation. The reason is threefold. First, there are existing architecture for conducting statistical validation and predictive validation. Topic modeling packages such as `text2vec` [@selivanov2020tex2vec] and `topicmodels` [@bettina2011topicmodels] provide functions to calculate metrics such as perplexity. Packages such as `textmineR` [@jones2019textminer], `stminsights` [@schwemmer2018stminsights] and `LDAvis` [@sievert2015ldavis] offers additional methods for statistical validation and predictive validation. As of writing, `tosca` [@koppers2020tosca] is the only package dealing with semantic validation. But the text-based interface might pose challenges to human annotators and it can only support topic models from one package [@change2015lda].

Second, results from statistical validation do not always agree with those from semantic validation. For example, topics from a topic model with a lower perplexity do not have a better interpretability [@chang2009reading]. Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g. semantic coherence [@mimno2011optimizing]. Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying. Nonetheless, conducting only statistical validation is not adequate because 3 validation operations supplement each other.

>>>>

This package focuses on semantic validation. The reason is threefold. First, there is existing architecture for conducting statistical validation and predictive validation. Topic modeling packages such as `text2vec` [@selivanov2020tex2vec] and `topicmodels` [@bettina2011topicmodels] provide functions to calculate metrics such as perplexity. Packages such as `textmineR` [@jones2019textminer], `stminsights` [@schwemmer2018stminsights] and `LDAvis` [@sievert2015ldavis] offers additional methods for statistical validation and predictive validation. As of writing, `tosca` [@koppers2020tosca] is the only package dealing with semantic validation. But the text-based interface might pose challenges to human annotators and it can only support topic models from one package [@change2015lda].

Second, results from statistical validation do not always agree with those from semantic validation. For example, a topic model with a lower perplexity does not have a better interpretability [@chang2009reading]. Of course, there are also metrics from statistical validation that are shown to be correlated with semantic validity, e.g. semantic coherence [@mimno2011optimizing]. Calculation of semantic coherence is recommended in the best practice paper by @maier2018applying. Nonetheless, conducting only statistical validation is not adequate because 3 validation operations supplement each other.
